---
title: "Automate your CV using R Markdown: Easy as 1, 2, knit"
description: |
  The first R-Ladies meetup of 2022! A workshop for building your CV using R Markdown and the R packages `datadrivencv`, `pagedown` & `vitae`. 
author: 
  - name: Shazia Ruybal-Pesántez
    url: https://shaziaruybal.com
    affiliation: Walter and Eliza Hall Institute & Burnet Institute
    affiliation_url: "https://www.burnet.edu.au/people/701_shazia_ruybal"
date: 2022-02-04
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r libraries}
library(distilltools)
```

```{r icon-links}
# [TODO]: fill in urls
# [TODO]: delete any unessary icons (or add more)
# [TODO]: css styling for .icon-link and .icon-link:hover
# [NOTE]: icons in same chunk will appear on same line
# [NOTE]: icons in different chunks will appear on a different lines
```

```{r}
icon_link(icon = "fab fa-meetup",
          text = "Register",
          url = "https://www.meetup.com/en-AU/rladies-melbourne/events/283353273/")

icon_link(icon = "fab fa-github",
          text = "Slides and materials",
          url = "")

icon_link(icon = "fas fa-play-circle",
          text = "Youtube video",
          url = "")
```


### About the event:

We are very excited to announce R Ladies Melbourne's first event of 2022! This event will be presented by [Dr. Shazia Ruybal-Pesántez](https://shaziaruybal.com), R Ladies Melbourne President and Postdoctoral Research Scientist at WEHI and Burnet Institute.

Updating your CV can be a tedious, but very necessary task! Most often this process involves creating and updating a user-created template in e.g. a Word document and fiddling with formatting for longer than one would like to admit, especially when it is time to update the content. With R Markdown, you can quickly turn your CV into a beautiful, automated document that is easy to produce, maintain and update to suit your specific needs. With this automated approach, the only thing you really have to worry about and devote your time to is writing the content.

In this talk, Shazia will take you through the R packages `datadrivencv`, `pagedown` and `vitae` that can be used with R Markdown to create and automate your CV. The aim is to guide you through how to save your data in a readable format for these packages, how to set up your R Markdown document, and how to render the output in different formats, all so that you can automate your pipeline to quickly and easily update your CV! This talk should give you sufficient information and materials that you can customize and either follow along during the talk or create your CV on your own after the talk.

### <i class="fab fa-meetup"></i> Event details: 

This will be an online event. Please connect to the zoom session at 12pm Melbourne time (AEDT) on Friday the 4th of February. [Register here](https://www.meetup.com/en-AU/rladies-melbourne/events/283353273/)
